Synthesizing Symmetric Lenses

### 2018-07-08 papers/SymmetricLenses/main.tex
made some eval changes

The cost of a lens between two SREs $c(\Lens, \Regex, \RegexAlt) =
\MaxOf{\LEntropyOf{\Regex \Given \Lens, \RegexAlt}} +
\MaxOf{\REntropyOf{\RegexAlt \Given \Lens, \Regex}}$ is the maximum sum of
recovering the left format from the right, and the right from the left. We have
proven theorems demonstrating the calculated entropy corresponds to the actual
conditional entropy to recover the data.\bcp{Again, the proofs should be
  included.}

@@

\paragraph*{Open and Closed Regular Expressions} While GreedySynth acts
relatively efficiently, it suffers from an exponential blowup when converting
regular expressions to DNF form.\sam{Perhaps explain why this blowup arises?} This can be minimized by not converting
\emph{all} of the regular expression into DNF form, but only converting
\emph{some} of it to DNF form. We add in an additional atom, where an atom can
be an either an iteration of a DNF regular expression or it can be a regular
expression. When converted into a DNF regular expression, if $\Regex$ is a
stochastic regular expression, annotated as closed, then $\ToDNFRegexOf{\Regex}
= \AtomToDNFOf{\Regex}$.

@@

\paragraph*{Compositional Synthesis} Compositional synthesis allows us to use
previously defined lenses - whether they are previously defined by users or by
synthesis. We alter \GreedySynth such that two regular expression atoms can be
mapped to each other either if they are the same regular expression and have
examples agreeing with the examples\bcp{What does ``have
examples agreeing with the examples'' mean??}, or if there is a lens which is a
composition of predefined lenses between them, where the lens alters the
examples in a desired way.

@@

We have extended Optician\bcp{this is the first mention of the word
  Optician!} with our symmetric synthesis algorithm. Users can 
write synthesis tasks alongside lens combinators, use those synthesis results in
the manual writing of new lenses, and use previously defined lenses in the
synthesis of new lenses.

In this evaluation, we aim to answer two primary questions:
\begin{enumerate}
\item Is our synthesis procedure efficient enough to be used in everyday
  development?  In particular, can it be used in place of the existing
  bijective lens synthesis algorithm integrated with Boomerang (which
  \citet{miltner+:bijective-synthesis} have argued is reasonably fast in
  practice)? 
  \item Are the heuristics we have described useful for reducing the 
  ``specification overhead'' for users?  \bcp{Maybe it would be better to
    ask {\em which} heuristics are the most useful.  Also, are we talking
    about reducing the number of examples needed?  It's not clear.  (And:
    Don't the heuristics also make it faster??)}
\end{enumerate}

\subsection{Benchmark Suite}
Our benchmarks are drawn from four different sources.\bcp{What makes this a good
  set of benchmarks for present purposes?}
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In adopting
  these benchmarks, we go beyond the data cleaning tasks\bcp{confusing: you
    say these are data cleaning tasks, then immediately say we go beyond
    data cleaning tasks.  (I know the next bit of the sentence makes it
    (somewhat) clearer, but the reader is already lost right here.)}, and
  synthesize 
  synchronization functions\bcp{what is a ``synchronization function''}
  between the ad-hoc data and their cleaned forms. 
  \bcp{Clarify:}Optician also adopted benchmarks from Flash Fill, but required alterations to
  be in bijective form\bcp{Mysterious}. With our symmetric enhancement, we
  \bcp{words missing?} Optician's four 
  benchmarks and 4 new Flash Fill benchmarks with no alterations.
\item We adapted \afm{29} benchmarks from Augeas.  These benchmarks are the same
  as those present in Optician.  \bcp{I (think I) understand what this
    means, but readers will not.}While these benchmarks had to be slightly
  adapted for bijectivity, previous work addressed this lack of bijectivity by
  synthesizing quotient bijective lenses~\cite{?}.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

\bcp{Why is this a good set of benchmarks for the purposes described earlier
in the section?}

\subsection{Efficiency}

To answer our first research question, we measure the runtime of our algorithm
and compare it to the existing algorithm for synthesizing bijective
lenses.\bcp{Note that this comparison doesn't, directly answer the question
  ``Is it fast enough.''}

We synthesized lenses in 4 modes:

\begin{tabulary}{\linewidth}{rL}
  \SSOpt{}: & We synthesize lenses using our symmetric synthesis algorithm with all optimizations enabled.\\
  \SSNCOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but compositional synthesis is not enabled.\\
  \BSOpt{}: &  We synthesize lenses using the existing bijective lens synthesis
              algorithm with all optimizations enabled\\
  \BSNCOpt{}: & We synthesize lenses using the existing bijective lens synthesis
                algorithm, but compositional synthesis is not enabled.\\
\end{tabulary}\\

We include running these algorithms without compositional synthesis to stress
test the algorithms. While compositional synthesis makes the procedure easier,
and demonstrates the potential to be used in arbitrarily hard problems, it is
dependent on the user identifying important sublenses between subcomponents of
the final formats. It is therefore interesting to see how many problems each
algorithm can solve, when trying to synthesize ``in one go.''

@@

The slowest completed benchmark for both the bijective and symmetric synthesis
algorithms is \texttt{xml\_to\_augeas.boom}, a benchmark that converts
arbitrary XML up to depth 3 into a serialized version of the structured
dictionary representation used in Augeas.  This benchmark takes 18.9 seconds for
the symmetric synthesis algorithm to complete, and 9.3 seconds the bijective
synthesis algorithm to complete.

\subsection{The Effect of Our Heuristic}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMCCOpt{}: & The lens cluster that contains is identified through \SSOpt{}. \GreedySynth is then called on that pair of SREs. \\
  \NMOpt{}: & Neither \GreedySynth nor \RXSearch have any notion of cost; they
              both merely search for
              any lens that satisfies the specification. 
\end{tabulary}

>>>>

The cost of a lens between two SREs $c(\Lens, \Regex, \RegexAlt) =
\MaxOf{\LEntropyOf{\Regex \Given \Lens, \RegexAlt}} +
\MaxOf{\REntropyOf{\RegexAlt \Given \Lens, \Regex}}$ is the maximum sum of
recovering the left format from the right, and the right from the left. We have
proven theorems demonstrating the calculated entropy corresponds to the actual
conditional entropy to recover the data.

@@

\paragraph*{Open and Closed Regular Expressions} While GreedySynth acts
relatively efficiently, it suffers from an exponential blowup when converting
regular expressions to DNF form. This can be minimized by not converting
\emph{all} of the regular expression into DNF form, but only converting
\emph{some} of it to DNF form. We add in an additional atom, where an atom can
be an either an iteration of a DNF regular expression or it can be a regular
expression. When converted into a DNF regular expression, if $\Regex$ is a
stochastic regular expression, annotated as closed, then $\ToDNFRegexOf{\Regex}
= \AtomToDNFOf{\Regex}$.

@@

\paragraph*{Compositional Synthesis} Compositional synthesis allows us to use
previously defined lenses - whether they are previously defined by users or by
synthesis. We alter \GreedySynth such that two regular expression atoms can be
mapped to each other either if they are the same regular expression and agree
with the examples, or if there is a lens which is a composition of predefined
lenses between them, where the lens agrees with the examples.

@@

We have extended the Optician synthesis plugin to Boomerang~\cite{?} with our
symmetric synthesis algorithm. In doing so, users can write synthesis tasks
alongside lens combinators, use those synthesis results in the manual writing of
new lenses, and use previously defined lenses in the synthesis of new lenses.

In this evaluation, we aim to answer three primary questions:
\begin{enumerate}
\item Is our synthesis procedure efficient enough to be used in everyday
  development?

\item How much slower do we perform on bijective lens synthesis benchmarks than
  the existing Optician system customized for bijective lenses.

\item Which heuristics we have described useful for reducing the ``specification
  overhead'' for users? In particular, which heuristics are useful in
  synthesizing the desired lens, instead of merely a lens that satisfies the
  specification.
\end{enumerate}

\subsection{Benchmark Suite}
Our benchmarks are drawn from three different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In these
  benchmarks, we not only provide functions that clean the data, but we also
  provide other synchronization functions: if the cleaned data is updated, those
  changes are reflected in the original format.
\item We adapted \afm{29} benchmarks from Augeas. These benchmarks turn the
  ad-hoc data present in Linux configuration files into a structured, dictionary
  representation.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

A realistic benchmarks suite is cretical in answering the first research
question. To determine whether our algorithm is fast enough to be used in
everyday development, we need to evaluate whether we can solve real-world
problems efficiently. All three of our benchmark sources test real life
problems: the data cleaning tasks presented in Flash Fill are either derived
from online help forums or taken from the Excel product team; Augeas is a
utility that transforms Linux configuration files into a manageable dictionary
form; the many of the remaining benchmarks are from synchronizing real-life data
formats, like BibTeX and EndNote.

\subsection{Useful in Everyday Development}

To answer our first research question, we measure the runtime of our algorithm
on our benchmark suite.

We synthesized lenses in 2 modes:

\begin{tabulary}{\linewidth}{rL}
  \SSOpt{}: & We synthesize lenses using our symmetric synthesis algorithm with all optimizations enabled.\\
  \SSNCOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but compositional synthesis is not enabled.\\
\end{tabulary}\\

We include running the symmetric synthesis algorithm without compositional
synthesis to stress test the algorithms. While compositional synthesis makes the
procedure easier, and demonstrates the potential to be used in arbitrarily hard
problems, it is dependent on the user identifying important sublenses between
subcomponents of the final formats. It is therefore interesting to see how many
problems each algorithm can solve, when trying to synthesize ``in one go.''

@@

\subsection{Slowdown Compared to Bijective Synthesis}

To compare to the existing bijective synthesis algorithm, we run our symmetric
synthesis algorithm on the original Optician benchmark suite. \afm{8} of these
benchmarks had to be slightly altered with tighter specifications or termination
parameters, as we had to alter the original specifications to generate the
correct lens.

To perform this comparison, we synthesized lenses in 2 modes:

\begin{tabulary}{\linewidth}{rL}
  \SSOpt{}: & We synthesize lenses using our symmetric synthesis algorithm with all optimizations enabled.\\
  \BSOpt{}: & We synthesize lenses using the existing bijective synthesis
              algorithm with all optimizations enabled.\\
\end{tabulary}\\

For each benchmark in our benchmark suite, we ran every mode on it with a
timeout of 30 seconds, and average the result over 5 runs.
Figure~\ref{fig:comparison-times} summarizes the results of these tests. On
average, \SSOpt{} took 2.1 times (\afm{3.5} seconds) longer to complete than
\BSOpt{}.

The slowest completed benchmark for both synthesis algorithms is
\texttt{xml\_to\_augeas.boom}, a benchmark that converts arbitrary XML up to
depth 3 into a serialized version of the structured dictionary representation
used in Augeas. This benchmark takes 18.9 seconds for the symmetric synthesis
algorithm to complete, and 9.3 seconds the bijective synthesis algorithm to
complete.

\subsection{The Effects of Our Heuristics}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMCCOpt{}: & The lens cluster that contains is identified through \SSOpt{}. \GreedySynth is then called on that pair of SREs. \\
  \NMOpt{}: & Neither \GreedySynth nor \RXSearch have any notion of cost; they
              both merely search for
              any lens that satisfies the specification. 
\end{tabulary}
